\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-01-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added new table and figure to manuscript

\begin{figure}[!hbt]
    \centering
    \small
    \includegraphics[width = \textwidth]{Figs/BoxPlot.pdf}
    \caption{MSE differences between base forecasts and reconciled forecasts using OLS, MinT and WLS, and also the bottom-up approach for $h = 1$. A positive value indicates that the coherent forecasts are an improvement over the base forecasts.}\label{fig:BaseVSRecon_Fc}
\end{figure}

\begin{table}[!hbt]
\caption {Average {MSE($\times 10^3$)} over all 140 rolling window replications for $h=1$.}\label{tab:AveraveDifferences}
  \centering \tabcolsep=0.4cm
  \begin{tabular}{lccccc}
  \toprule
          & Base & OLS & MinT & WLS & Bottom-up \\
   MSE    & 4.31 & 4.20 & \textbf{4.16} & 4.48 & 5.28 \\
  \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{figure}[!hbt]
    \centering
    \small
    \includegraphics[width = \textwidth]{Figs/lossboxplots_1.pdf}
    \caption{Differences between base forecasts and reconciled forecasts for different loss functions using different reconciliation methods for $h = 1$. A positive value indicates that the coherent forecasts are an improvement over the base forecasts.}\label{fig:BaseVSRecon_Fc}
\end{figure}

%\begin{table}[!hbt]
%\caption {Average {MSE($\times 10^3$)} over all 140 rolling window replications for $h=1$.}\label{tab:AveraveDifferences}
%  \centering \tabcolsep=0.4cm
%  \begin{tabular}{lccccc}
%  \toprule
%          & Base & OLS & MinT & WLS & Bottom-up \\
%   MSE    & 4.31 & 4.20 & \textbf{4.16} & 4.48 & 5.28 \\
%  \bottomrule
%  \end{tabular}
%\end{table}
\input{Tables/lossvmethods_h_1.tex}
